Response to the defense feedback

### 2021-05-27 changelog.tex
Updates from Overleaf

\title{Changelog}
\author{Qinkun Bao}
\date{May 2021}

@@

On the other hand, there are many success stories with dynamic tools (e.g., SAGE, AFL, Valgrind) in recent years. In particular, fuzzing is becoming a hot trend these years, especially after DARPA CGC in 2016. The fuzzing method is suitable for a task such as side-channel detection. If a program executes two different code paths or accesses two different variables with two different input values, the program is vulnerable to side-channel attacks. When we report the leakages sites to developers, we can tell them the two inputs. Developers can quickly reproduce the leakage sites with the inputs.  Interestingly, there are a few (not many) related papers. That's why I used fuzzing at the beginning of the project.

@@

It is hard to explain Entropy. There is a rumor about entropy between John von Neumann and Claude Shannon. When Shannon developed the concept of information theory, he did not have a good idea to name the measurement of uncertainty in a system. Neumann told Shannon, ``You should call it entropy, for two reasons. In the first place,your uncertainty function has been used in statistical mechanics under that name, so it already has a name. In the second place, and more important, nobody knows what entropy really is, so in a debate you will always have the advantage.'' In my dissertation proposal, everyone does not really understand how we quantify the amount of leaked information in Abacus. In my final defense, everyone is confused with the term ``lower bounds'' except my advisor.

@@

a. I revised the description in Chapter 5. I avoided the use of ``term lower bound''.

>>>>

\title{Response to the defense feedback}
\author{Qinkun Bao}
\date{May 2021}

@@

On the other hand, there are many success stories with dynamic tools (e.g., SAGE, AFL, Valgrind) in recent years. In particular, fuzzing is becoming a hot trend these years, especially after DARPA CGC in 2016. The fuzzing method is suitable for a task such as side-channel detection. If a program executes two different code paths or accesses two different variables with two different input values, the program is vulnerable to side-channel attacks. When we report side-channel leakages sites to developers, we can tell them the two inputs. Developers can quickly reproduce the leakage sites with the inputs.  Interestingly, there are a few (not many) related papers. That's why I used fuzzing at the beginning of the project.

@@

It is hard to explain Entropy. There is a rumor about entropy between John von Neumann and Claude Shannon. When Shannon developed the concept of information theory, he did not have a good idea to name the measurement of uncertainty in a system. Neumann told Shannon, ``You should call it entropy, for two reasons. In the first place,your uncertainty function has been used in statistical mechanics under that name, so it already has a name. In the second place, and more important, nobody knows what entropy really is, so in a debate you will always have the advantage.'' During my dissertation proposal, everyone does not really understand how we quantify the amount of leaked information in Abacus. In my final oral exam, everyone is confused with the term ``lower bounds'' except my advisor.

@@

a. I revised the description in Chapter 5. I avoided the use of term ``lower bound''.
